Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

\begin{abstract}
\textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only five years. Here we develop and evaluate \textcolor{blue}{an} automated synthesis approach to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered in the model. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house}. 
We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis. We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
\end{abstract}

@@

Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using software model checking as a backend verification engine~\cite{DBLP:journals/corr/abs-1909-13139}. The analytical method of optimization was adopted.

@@

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year. Some HOMER Pro drawbacks were also noted. (1) System equipment does not include an explicit charge controller. HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement. However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing. (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with an $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types. (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.

@@

HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial. The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf. Moreover, our synthesis approach considers surge power demand from the house, which is not viewed by HOMER Pro or PVsyst. This feature is a definite advantage of the formal synthesis method. HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis. The formal synthesis method, therefore, presents more reliable results than HOMER Pro.

>>>>

\begin{abstract}
\textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only five years. Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement costs and the operation \& maintenance costs over a 20-year period. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}. We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market \textcolor{blue}{for PV systems}. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
\end{abstract}

@@

Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems. It uses  software model checking as a backend verification engine~\cite{DBLP:journals/corr/abs-1909-13139}. The analytical method of optimization was adopted.

@@

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year. Some HOMER Pro drawbacks were also noted. (1) System equipment does not include an explicit charge controller. HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement. However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing. (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with an $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types. (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel. \textcolor{blue}{The cost of every equipment item used in HOMER Pro is an US-based cost, without adaptation regardless of where the equipment is installed.}

@@

\textcolor{blue}{Related to the cost (LCC) present by both tools, HOMER Pro do not use the real cost for PV systems deployed in Brazil; therefore the optimal solution presented by HOMER Pro is notoriously cheaper than our technique. However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated.}

\textcolor{blue}{Besides that,} HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, but it is not commercial. The proposed synthesis tool, however, presents inverters that are commercial and can be obtained off-the-shelf. Moreover, our synthesis approach considers surge power demand from the house, which is not viewed by HOMER Pro or PVsyst. This feature is a definite advantage of the formal synthesis method. HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis. The formal synthesis method, therefore, presents more reliable results than HOMER Pro.

### 2020-07-06 Tex/CAV2019/replyVSTTEJUNE2020.tex
VSTTE rebuttal

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. Indeed, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. The paper was reviewed and the PV sizing modelling was changed to a more higher level of explanation. Different parts of the above mentioned sections in blue indicate where we changed/reviewed the text.

@@

\begin{resposta} 
We thank the reviewer again for this insightful comment and suggestion. Indeed, we had to revise every section of the paper in order to address the specific issues highlighted by the reviewer......
Alessandro: Pra mim, é o desenvolvimento de uma técnica (como já discutimos em janeiro), que usa model checking e, como é feita em duas etapas, ela lembra o modo como o CEGIS funciona. E como o resultado é uma solução ótima, o resultado é uma otimização. Creio que isto deva ir pra introdução também (e pro abstract).

@@

\begin{resposta} 
Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica. \textbf{Que achas?}  \textbf{Lucas: Concordo. Nao poderia aplicar uma busca binaria como fizemos no nosso journal do IJES?} 
acrescentei busca binária e $\nu Z$ na conclusão.

@@

\begin{resposta} 
Alessandro: Essa questão é para se pensar. Pra mim, a não linearidade das equações do artigo anterior de validação de sistemas solares estava mais claro pois usamos equações exponenciais e logaritmas. Nesse, a não linearidade se deve ao fato de a curva do ótimo global não ser contínua, pois pegamos valores específicos de variáveis não determinísticas, valores inteiros...daí eu não sei responder o que o revisor questionou.

Lucas: Modelamos essas usando aritmética de ponto flutuante. É apenas uma aproximação dos números reais. No entanto, neste trabalho, não nos preocupamos em calcular o erro de arredondamento. Precisamos enfatizar isso no texto. Esse nosso paper descreve um pouco sobre esses erros: https://arxiv.org/pdf/2004.12699.pdf

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. He/she is right and it was the same observation did by Reviewer \#1. In order to correct this issue, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. The paper was reviewed and the PV sizing modelling was passed to a more higher level of explanation. Different parts of the paper in blue indicate where we changed/reviewed the text.

@@

\begin{resposta}
Preciso pensar aqui

@@

\begin{resposta}
The reviewer is right, we missed the details about why those values are taken. Therefore we reviewed the text to: "The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime".
\end{resposta}

@@

\begin{resposta}
We have updated the entire paragraph to explain the meaning of these variables as follows: ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq. (9) for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.''
\end{resposta}

@@

\begin{resposta} 
Repete o revisor 1. As mudanças que farei matam essas questões
\end{resposta}

 I do have some doubts about suitable the encodings that
  the authors choose, in particular, how relevant full fledged
  floating point reasoning is, but have no way to check.
  For a conference paper I am quite willing to give the paper a
  pass on this doubt as exposing details in the encodings could
  make the paper even less accessible.
- The paper contains several awkwardly formulated sentences. Examples
  are listed below.

>>>>

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. Indeed, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. The paper was reviewed and the PV sizing modelling was changed to a higher level of explanation, with a flowchart. The Algorithm's pseudo-code followed the same idea. Besides that, in case of interest about the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF file that can be accessed as well.

@@

\begin{resposta} 
We thank the reviewer again for this insightful comment. Indeed, we had to revise some specific parts of the paper where CEGIS, technique, or optimization appeared (Abstract, Introduction, and Background sections). Our proposal is a technique, that is based on CEGIS when we consider the use of synthesis and automated verification, and we aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization). We expect that the reviewed text can clarify the issue.

@@

\begin{resposta} 
We will try to clarify this issue. We use 4 nondeterministic variables hold the position of 4 matrices with complete datasheet information from a equipment item. We have 4 variables and 4 matrices: one to PV panels, one to batteries, one to inverter, and one to the charge controller. Those nondeterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}: this is the phase {\sc Synthesize} of the technique. For the {\sc Verify} phase, is performed a linear search for the lowest cost, and the search is based in FAIL or SUCCESS check from a cost that is linearly incremented in this model. The model checking is used during this {\sc Verify} phase: if the process FAIL then a optimal solution is found, if SUCCESSES then there is not a feasible solution from the equipment list inputted of the technique. We added a future work at the end of the CONCLUSIONS section, related to the possibility of speed up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).

@@

\begin{resposta} 
We model these PV sizing constraints using floating point arithmetic. It is just an approximation of the real numbers. However, in this work, we are not concerned with calculating the rounding error, which is negligible when we consider the size of the physical quantities and the variables adopted. We added this information at the end of section 2.2. Therefore, we thank you the question and the possibility to clarify this issue in the paper.

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. He/she is right and it was the same observation did by Reviewer \#1. We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. The paper was reviewed and the PV sizing modelling was changed to a higher level of explanation, with a flowchart. The Algorithm's pseudo-code followed the same idea. Besides that, in case of interest about the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.

@@

\begin{resposta}
Indeed the optimal sizing means the lowest cost from a feasible (technical) solution. When we compare just the LCC you are right: HOMER Pro produces the lowest values in mostly case-studies. However, we prove that using a simulation tool (PVsyst) with the optimal produced from our technique and from HOMER, that our technical solution is better to meet the house's requirements. We added two sentences in order to clarify this issue.

In section 4.4 Results: "The cost of every equipment item used in HOMER Pro is an US-based cost, without adaptation regardless of where the equipment is installed."

In section 4.5 Comparison Between Formal Synthesis and HOMER Pro: "Related to the cost (LCC) present by both tools, HOMER Pro do not use the real cost for PV systems deployed in Brazil; therefore the optimal solution presented by HOMER Pro is notoriously cheaper than our technique. However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated."

@@

\begin{resposta}
The reviewer is right, we missed the details about why those values are taken. Therefore we reviewed the complementary online text to: "The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime".
\end{resposta}

@@

\begin{resposta}
We have updated the entire paragraph in the complementary online file to explain the meaning of these variables as follows: ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq. (9) for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.''
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. Those are the same observations did by Reviewer \#1 and \#2. We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. The paper was reviewed and the PV sizing modelling was changed to a higher level of explanation, with a flowchart. The Algorithm's pseudo-code followed the same idea. Besides that, in case of interest about the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.

 I do have some doubts about suitable the encodings that
  the authors choose, in particular, how relevant full fledged
  floating point reasoning is, but have no way to check.
  For a conference paper I am quite willing to give the paper a
  pass on this doubt as exposing details in the encodings could
  make the paper even less accessible.

\begin{resposta}
Related to the floating point reasoning: we model the PV sizing constraints using floating point arithmetic. It is just an approximation of the real numbers. However, in this work, we are not concerned with calculating the rounding error, which is negligible when we consider the size of the physical quantities and the variables adopted. We added this information at the end of section 2.2. Therefore, we thank you the question and the possibility to clarify this issue in the paper.
\end{resposta}

- The paper contains several awkwardly formulated sentences. Examples
  are listed below.
